---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "##",
                      fig.retina = 2,
                      fig.path = "README_figs/README-")
```

# Installation

Until now the package is not in CRAN but you can download it via GitHub with the following command:

```{r, eval = FALSE}
if (!require("devtools"))
  install.packages("devtools")
devtools::install_github("JohannesFriedrich/EcoCounteR")
```


# Introduction

The **R**-package *EcoCounteR* is an API wrapper for data collected by https://www.eco-compteur.com. You can request available data from different Eco Counter installations by submitting the Id of the installation to different functions:

Function name       | Description                                        | Example
--------------------|----------------------------------------------------| -------
get_EcoCounter_info | request common information about an installation  | get_EcoCounter_info(100020207)
get_EcoCounter_location | request location of an installation  | get_EcoCounter_location(100020207)
get_EcoCounter_data | request data from an installation  | get_EcoCounter_info(101020207)

The following chapters show some examples how to use the **R**-package *EcoCounteR*.

# Request basic information from Eco Counter API <a id="basic_information"></a>

First we load some needed packages. The function `get_EcoCounter_info()` will deliver some information about an installation located at Calgary in the Stephen Avenue. The only argument in `get_EcoCounter_info()` is the Id of the installation.

```{r, warning=FALSE, message=FALSE}
library(EcoCounteR)
library(leaflet)
library(htmltools)

EcoCounterId <- 100020207
info <- get_EcoCounter_info(EcoCounterId)
```


```{r, eval = FALSE}
info
```

```{r echo=FALSE}
knitr::kable(
  info[,1:3],
  format = "html"
)
```


For later requests we need the coloumn `id` to get data from this specific installation.

The function `get_EcoCounter_info()` can also handle multiple EcoCounterIds, e.g.:

```{r}
EcoCounterIds = c(100020207, 100017181)

info <- get_EcoCounter_info(EcoCounterIds)
```

```{r, eval = FALSE}
info
```

```{r echo=FALSE}
knitr::kable(
  info[,1:3],
  format = "html"
)
```

# Map location of an installation

To get an overview of the installations, we can use the function `get_EcoCounter_location()`. This function extracts the coordinates from the installations. We can insert the result directly to the **R**-package `leaflet`.


```{r get_location}
get_EcoCounter_location(EcoCounterIds) %>% 
leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>% 
  addTiles() %>%  
  addMarkers(~long, ~lat, popup = ~htmltools::htmlEscape(name))
```

# Request data from Eco Counter API

Now we can use the extracted information to request data. First we load some packages which help to analyse and visualise data.

```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(scales)
```

From section [2](#basic_information) we know different sub-Ids of an installation. We allocate the different sub-Ids:

```{r set_Ids}
Stephan_Avenue_Ped <- 101020207
Stephan_Avenue_Bike <- 102020207
Stephan_Avenue_Car <- 103020207
```

Now it's time to request some data. For that purpose the function `get_EcoCounter_data()` can be used. The function takes just one required argument: EcoCounterId. **Note: This is not the same EcoCounterId as inserted in `get_EcoCounter_data()`and `get_EcoCounter_location()`**.
The function `get_EcoCounter_data()` can take more arguments to specify the request. 

| Argument                       | Description | Example |
|--------------------------------| -----------------------------| ------------------ |
| EcoCounterId | sub-Id to request specific installation | 101020207 |
| from | Start date of the requested data in the form "YYYYMMDD" | "20180101" |
| to | End date  of the requested data in the form "YYYYMMDD" | "20180110" |
| step | Frequency of saved data: 2 (15 min), 3 (hourly), 4 (daily), 5 (weekly), 6 (monthly), 7 (yearly) | step = 3|

Some examples:

```{r eval=FALSE}
## get daily saved data for the day before yesterday and yesterday
get_EcoCounter_data(101020207)

## get daily saved data from  1st January 2018 until yesterday |
get_EcoCounter_data(101020207, from = "20180101")

## get hourly saved data from  1st January 2018 to 10th January 2018 |
get_EcoCounter_data(101020207, from = "20180101", to = "20180110", step = 3)
```

Now let's put things into practical terms. 
We request data from 1st to 20th January 2018. With `mutate(Type = XXX)` we add a new coloum to the data.frame with the specific type of request.

```{r}
Stephan_Avenue_Ped_daily <- get_EcoCounter_data(Stephan_Avenue_Ped, from = "20180101", to = "20180120") %>% 
  mutate(Type = "Pedestrains")

Stephan_Avenue_Bike_daily <- get_EcoCounter_data(Stephan_Avenue_Bike, from = "20180101", to = "20180120") %>% 
  mutate(Type = "Bikes")

Stephan_Avenue_Car_daily <- get_EcoCounter_data(Stephan_Avenue_Car, from = "20180101", to = "20180120") %>% 
  mutate(Type = "Cars")

Stephen_Avenue_complete <- bind_rows(Stephan_Avenue_Ped_daily, Stephan_Avenue_Bike_daily, Stephan_Avenue_Car_daily)
```

In the last line all single data.frames are combined to a single data.frame. You can further analyse this data to your own needs, e.g. find the days with the most appearance per type:

```{r}
Stephen_Avenue_complete %>% 
  group_by(Type) %>% 
  top_n(1, comptage)
```

# Visualise Data

The following examples shows the visualisation of the data.

```{r plot_Stephen_Avenue, message=FALSE}
g <- ggplot(Stephen_Avenue_complete, aes(x = date, y = comptage, fill = Type)) +
  geom_bar(stat = "identity") +
  scale_x_datetime(labels = date_format("%d.%m.%Y")) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))

plot(g)

g2 <- g +
  scale_x_datetime(labels = date_format("%d.%m.%Y")) +
  facet_wrap(~Type, scales = "free_y") +
  geom_smooth(show.legend = FALSE) + 
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))

plot(g2)
```
